### 2015-05-13 whoop.tex
fix

The simple concurrent programming model of \S\ref{sec:symbolicpairwise} is deliberately idealistic to make it easy to describe our symbolic verification technique. In practice, Linux drivers are written in C, we do not know up-front which are the entry points for a driver, drivers do not work with a cleanly specified set of named locks, and rather than having a given set of named shared variables, we have arbitrary memory accesses via pointers. We now explain how we have taken the conceptual ideas from \S\ref{sec:symbolicpairwise} and used them to build \whoop, a practical, fully automatic tool for soundly detecting data races in drivers.

>>>>

The simple concurrent programming model of \S\ref{sec:symbolicpairwise} is deliberately idealistic to make it easy to describe our symbolic verification technique. In practice, Linux drivers are written in C, we do not know up-front which are the entry points for a driver, drivers do not work with a cleanly specified set of named locks, and rather than having a given set of named shared variables, we have arbitrary memory accesses via pointers. We now explain how we have taken the conceptual ideas from \S\ref{sec:symbolicpairwise} and used them to build \whoop, a practical, fully automatic tool for detecting data races in drivers.
